Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-16 README.Rmd
updated to do list

- Manuscript
  - Adjust order of match and non-match in feature heat map
  - Train a random forest model on prepared training data (make sure to set a seed!) 
  - Make predictions on test data
  - Rerun all code in manuscript (check for changes in results)
  - Update text in manuscript to describe the random forest model process
  - Update all files in the submission folder
- Submission
  - Edit dataset descriptions in README and add to the readme.txt document for submission
  - Upload the files for submission and submit

@@

When the manuscript is knit, various files will be generated (such as `data-bullet-explain.rds` and `figure-10-1.png`). The first time the manuscript is knit, it will take a while (approximately 45 minutes on Katherine's computer). Once these files have been generated during the first knit, the manuscript will take much less time to knit (approximately 1 minute on Katherine's computer).

>>>>

- Manuscript
  - Determine what to do about random forest in paper
- Submission
  - Edit dataset descriptions in README and add to the readme.txt document for submission
  - Update all files in the submission folder
  - Upload the files for submission and submit

@@

When the manuscript is knit, various files will be generated (such as `data-bullet-explain.rds` and `figure-10-1.png`). The first time the manuscript is knit, it will take a while (possibly up to several hours). Once these files have been generated during the first knit, the manuscript will take much less time to knit (approximately a few minutes).
